### 2023-12-03 main.tex
''

For the single species case,  the solution of the exclusion process with open boundaries \cite{derrida1993exact,1993JSP....72..277S} has been of crucial importance in our understanding of the structural properties of non-equilibrium state, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviations \cite{mallick2022exact,bodineau2005current}. One may argue that the results available for the exclusion process are rooted in the algebraic symmetries of the corresponding integrable spin $s=1/2$ Heisenberg chain [SCHUTZ,RAGOUCY].

@@

\section{Duality}\label{sectionDuality}
In this section we prove the first main result of this paper. We show that the multispecies stirring process with open boundaries
can be studied by means of a dual process. After recalling the definition of duality between two
Markov processes in Section~\ref{def-duality}, we formulate our duality result  in Theorem~\ref{thm-duality}. A proof of the theorem is given in Section~\ref{proof-th-duality}.
The duality result yields several simplifications, \todo{which else?} the main one being that the
dual process has absorbing sites. Therefore, as shown in Corollary~\ref{Corolollary-ABS_Corr-abstract}, the study of correlations in the non-equilibrium steady state of the multispecies stirring process with open boundaries
is reduced to the study of the absorption probabilities of dual particles.

@@

@@

\todo{something wrong...}

@@

\todo{what happens to $q_N$?}

@@

\todo{somehow this now has extra index for the space and everywhere else not.... please fix}

@@

{\color{blue}where the expectation is take with respect to the non-equilibrium steady state distribution, i.e. it is given in \eqref{exactCorrelations}.}

@@

@@

Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ we obtain \eqref{implicit-mass-function}. 

>>>>

For the single species case,  the solution of the exclusion process with open boundaries \cite{derrida1993exact,1993JSP....72..277S} has been of crucial importance in our understanding of the structural properties of non-equilibrium state, such as long-range correlations \cite{spohn1983long} and non-local density large deviation functions \cite{derrida2007non,derrida1998exact} and current large deviations \cite{mallick2022exact,bodineau2005current}. One may argue that the results available for the exclusion process are rooted in the algebraic symmetries of the corresponding integrable spin $s=1/2$ Heisenberg chain \cite{schutzManyBody,SSEPReviewRagoucy}.

@@

\section{Duality}\label{sectionDuality}
In this section we prove the first main result of this paper. We show that the multispecies stirring process with open boundaries
can be studied by means of a dual process. After recalling the definition of duality between two
Markov processes in Section~\ref{def-duality}, we formulate our duality result  in Theorem~\ref{thm-duality}. A proof of the theorem is given in Section~\ref{proof-th-duality}.
The duality result yields {\color{blue} to a dual process that} %several simplifications,  the main one being that the
%dual process
 has absorbing sites\todo{which else?}. Therefore, as shown in Corollary~\ref{Corolollary-ABS_Corr-abstract}, the study of correlations in the non-equilibrium steady state of the multispecies stirring process with open boundaries
is reduced to the study of the absorption probabilities of dual particles.

@@

\begin{equation}\label{bosonic_2}

@@

\todo{something wrong...} {\color{blue} [I have added the vector at site $u(x)$]}

@@

\todo{what happens to $q_N$?} {\color{blue} we used the orthogonality between $\langle q_{1}^{u(x)} ,\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,q_{N}^{u(x)}\rangle=1$ on the extra-site $u(x)$}

@@

\todo{somehow this now has extra index for the space and everywhere else not.... please fix} {\color{blue} We have defined the bosonic operator with the extra-site, see under equation \eqref{bosonic_2}}

@@

{\color{blue}where the expectation is taken with respect to the non-equilibrium steady state distribution, i.e. it is given in \eqref{exactCorrelations}.}

@@

\begin{align}\label{sum}

@@

Therefore, using the linearity of the expectation and introducing the index $b\in \{0,\ldots,L\}$ {\color{blue} we rewrite the sum in equation \eqref{sum} as} \eqref{implicit-mass-function}.{\color{blue} Indeed, when $b>L-\ell$ we have vanishing terms in the sum \eqref{implicit-mass-function}.}
